\section{Discussion}
\label{sec:discussion}

The project is successful overall. We learned valuable lessons throughout. They are about both general research and visualization research.
\begin{itemize}
\item Knowing what's out there in the field is important. Researchers at entry level often start out experimenting their own thoughts without studying literatures. Reference is more than citation. Readers will not be convinced unless we can relate other people's work to ours and explain why, how, and what we are doing differently.
\item During this project, we find it really helpful to summarize the problems of published papers. These problems serve as good reminders of common pitfalls even for experienced researchers and reviewers. We also think going back to the first slides at the beginning of semester to be useful. It helps keep the project going in a regular track.
\item For the coding part, d3 is a quite different language from C-style ones. We started out skimming preliminary tutorials and moved on to modify the gallery codes. This approach turned out to be inefficient and painful. I personally misunderstood chaining methods until mid term. If one happens to be familiar with C-style languages like me, d3 is likely to deserve more time to acquire than you anticipate.
\item Time management is crucial. It's dangerous to wait till last minute. We usually set for ourselves a dummy deadline, one or two days prior to the real deadline. We thus apply major fixes early and have enough time for minor fixes in a relaxed mood, which actually improves the quality of those minor fixes.
\end{itemize}

